Supporting Information: Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2020-01-01 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Better explanations of beta

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{array}
\usepackage{multirow}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

@@

  \maketitle
  \graphicspath{{./supporting_figures/}}
  \bibliographystyle{ieeetr}

@@

  % mimic this
  \texttt{/setup/parameterize.py}            & 2.1 & Parameterize liquid crystal monomers and solutes with GAFF \\ \hline
  \texttt{/setup/build.py}                   & 2.1 & Build simulation unit cell \\ \hline
  \texttt{/setup/place\_solutes\_pores.py}   & 2.1 & Place equispaced solutes in the pore centers of a unit cell \\\hline
  \texttt{/setup/equil.py}                   & 2.1 & Equilibrate unit cell and run production simulation \\\hline
  \texttt{/analysis/solute\_partitioning.py} & 2.1 & Determine time evolution of partition of solutes between pores and tails \\\hline
  \texttt{/timeseries/msd.py}                & 2.2 & Calculate the mean squared displacement of solutes \\\hline
  \texttt{/analysis/sfbm\_parameters.py}     & 2.2 & Get subordinated fractional Brownian motion parameters by fitting to a solute's dwell and hop length distributions and positional autocorrelation function. \\\hline
  \texttt{/timeseries/ctrwsim.py}            & 2.2 & Generate realizations of a continuous time random walk with the user's choice of dwell and hop distributions \\\hline
  \texttt{/timeseries/forecast\_ctrw.py}     & 2.2 & Combines classes from \texttt{sfbm\_parameters.py} and \texttt{ctrwsim.py} to parameterize and predict MSD in one shot. \\\hline
  \texttt{/analysis/ markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_equilibration.pdf}
  \caption{}\label{fig:URE_equilibration}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_equilibration.pdf}
  \caption{}\label{fig:GCL_equilibration}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_equilibration.pdf}
  \caption{}\label{fig:ACH_equilibration}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_equilibration.pdf}
  \caption{}\label{fig:MET_equilibration}
  \end{subfigure}
  \caption{We considered a system to be equilibrated when the partition of solutes
  between the tails and pore plateaued. Our chosen equilibration point for each
  solute is indicated by the vertical black dashed line. (a) Urea equilibrates
  the fastest, after 1000 ns. (b) Ethylene glycol equilibrates after 1200 ns 
  (c) Acetic Acid does not equilibrate until 4400 ns. (d) We considered methanol
  to be equilibrated after 3500 ns. Methanol nearly completely partitions into
  the tails.}\label{fig:equilibration}
  \end{figure}

@@

  \newpage
  \section{Estimating the Hurst Parameter}\label{section:H_estimate}

@@

  % /supporting_figures/hurst_autocorrelation.py
  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{hurst_autocorrelation.pdf}
  \caption{The analytical autocorrelation function of FBM decays to zero faster when 
  H $<$ 0.5 compared to when H $>$ 0.5.}\label{fig:hurst_autocorrelation}
  \end{figure}

  The autocovariance function of fractional L\'evy motion is different from fractional
  Brownian motion (see Equations~\ref{M-eqn:fbm_autocorrelation}
  and~\ref{M-eqn:flm_autocovariance} of the main text), but their autocorrelation 
  structures are the same. The autocovariance function of FLM is dependent on the 
  expected value of squared draws from the underlying L\'evy distribution, $E\big[L(1)^2\big]$. 
  This is effectively the distribution's variance, which is undefined for most 
  L\'evy stable distributions due to their heavy tails. As a consequence, one should 
  expect $E\big[L(1)^2\big]$ to grow as more samples are drawn from the distribution
  with the autocovariance function responding accordingly. 
  However, we are only interested in the autocorrelation function. In order to predict
  the Hurst parameter from the autocorrelation function, we must show that it has 
  a well-defined structure and is independent of the coefficient in 
  Equation~\ref{M-eqn:flm_autocovariance} of the main text. In Figure~\ref{fig:flm_autocorrelation}, 
  we plot the average autocorrelation function from an FLM process with an increasing 
  number of observations per generated sequence. For all simulations we set $H$=0.35 
  and $\alpha$=1.4. The variance-normalized autocovariance function, i.e. the autocorrelation
  function, does not change with increasing sequence length. Additionally, the
  autocorrelation function of FBM, with the same $H$, is the same.

  % supporting_figures/flm_autocov.py
  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{flm_autocovariance.pdf}
  \caption{The autocorrelation function of an FLM process does not change with 
  increasing sequence length (N). It shares the same autocorrelation function as
  fractional Brownian motion (FBM). All sequenced used to make this plot were 
  generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:flm_autocorrelation}
  \end{figure}

@@

  \textit{Determining where to truncate the hop distribution:} A pure
  L\'evy stable distribution has heavy tails which can lead to arbitrarily
  long hop lengths. Our distribution of hop lengths fits well to a L\'evy
  distribution near the mean, but under samples the tails. In 
  Figure~\ref{fig:truncation_correction} we compare the empirically 
  measured transition emission distribution of the MSDDM for Urea to its maximum likelihood fit to
  a L\'evy stable distribution. The ratio between the two distributions 
  at each bin is nearly 1 close to the center, indicating a near-perfect
  fit, larger than 1 slightly further from the center, suggesting that 
  we slightly over sample intermediate hop lengths, and below 1 far from 
  the center, indicating under sampling of extremely long hop lengths.
  Based on the plot, we chose a cut-off of 0.8 nm in order to compensate for
  over sampled intermediate hop lengths. We used the same procedure
  to determine truncation parameters for all solutes.

  This procedure is complicated by the correlation structure of FLM. At a high level,
  Stoev and Taqqu use Riemann-sum approximations of the stochastic integrals defining
  FLM in order to generate realizations. They do this efficiently with the help of 
  Fast Fourier Transforms. In practice, this requires one to Fourier transform a zero-padded
  vector of random samples drawn from the appropriate L\'evy stable distribution, multiply
  the vector in Fourier space by a kernel function and invert back to real space. The end
  result is a correlated vector of fractional L\'evy noise.

  If one is to truncate an FLM process, one can apply the simple procedure above for 
  drawing uncorrelated values from the marginal L\'evy stable distribution, but after
  adding correlation, the maximum drawn value is typically lower than the limit set 
  by the user. Additionally, the shape of the distribution itself changes. Analogous
  to the database used to correct the Hurst parameter, we created a database to 
  correct the input truncation parameter (the maximum desired draw). The database
  returns the value of the truncation parameter that will properly truncate the
  output marginal distribution based on $H$, $\alpha$ and $\sigma$ (the width parameter).
  Figure~\ref{fig:truncation_correction} shows the result of applying our correction.
  Note that generating this database requires a significant amount of simulation and
  still likely doesn't perfectly correct the truncation parameter. The output leads
  to a somewhat fuzzy, rather than abrupt, cut-off of the output distribution. This 
  is likely beneficial since we observe a small proportion of hops longer the chosen
  truncation cut-off. When the cut-off value is close to the L\'evy stable $\sigma$ parameter,
  as it is in our anomalous diffusion models, we observed that the tails of the 
  truncated distribution tend to be undersampled. In order to maintain the distribution's 
  approximate shape up to the cut-off value we recommend ensuring that the cut-off
  value is at least 2 times $\sigma$. However, this may lead to a slight over-prediction
  of the MSD.

@@

@@

  To derive an analytical equation for the mean first passage time as calculated
  in the main text, first consider an initial pulse spreading out over time with
  a fixed mean. We can solve for the time-dependent probability density of 
  particle positions by solving the one dimensional diffusion equation:
  \begin{equation}
  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
  \end{equation}
  The appropriate initial and boundary conditions are:
  $$BC1: t > 0, z = \infty, p = 0$$
  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
  $$IC: t = 0, c = M\delta(z)$$
  where $M$ is the total number of particles in the system. It has been shown 
  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
  \end{equation}
  We can make the substitution $z = z - vt$, where $v$ represents a constant average
  velocity, in order to linearly shift the mean as a function of time:
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
  \end{equation}
  One can track the fraction of particles, $F$, that have crossed the pore 
  boundary by integrating:
  \begin{equation}
  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
  \end{equation}
  where $L$ is the pore length. This represents the cumulative first passage 
  time distribution so we take its derivative in order to arrive at the first
  passage time distribution:
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. We calculated the
  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT.

@@

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_trajectories.pdf}
  \caption{}\label{fig:GCL_solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/distributions_sfbm.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:GCL_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_powerlaw.pdf}
  \caption{}\label{fig:GCL_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_hop_acf.pdf}
  \caption{}\label{fig:GCL_hop_acf}
  \end{subfigure}
  \caption{For ethylene glycol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
  for ethylene glycol. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
  in the main text for a more detailed discussion.}\label{fig:GCL_anticorrelated_hops}
  \end{figure}

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_trajectories.pdf}
  \caption{}\label{fig:ACH_solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/distributions_sfbm.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
  \caption{}\label{fig:ACH_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
  \caption{}\label{fig:ACH_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
  \caption{}\label{fig:ACH_hop_acf}
  \end{subfigure}
  \caption{For acetic acid: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
  for acetic acid. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
  in the main text for a more detailed discussion.}\label{fig:ACH_anticorrelated_hops}
  \end{figure}

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_trajectories.pdf}
  \caption{}\label{fig:MET_solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/distributions_sfbm.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
  \caption{}\label{fig:MET_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
  \caption{}\label{fig:MET_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
  \caption{}\label{fig:MET_hop_acf}
  \end{subfigure}
  \caption{For methanol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
  for methanol. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
  in the main text for a more detailed discussion.}\label{fig:MET_anticorrelated_hops}
  \end{figure}

@@

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
  \caption{Urea}\label{fig:URE_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
  \caption{Methanol}\label{fig:MET_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
  \end{subfigure}
  \caption{The ensemble of solute trajectories may be stationary if the MSD
  calculated from different portions of the trajectory are the same. Here we
  plot the MSD calcluated up to a 500 ns time lag of the first and second
  halves of the equilibrated solute trajctories. Urea and acetic acid have
  similar MSDs, providing evidence of stationarity, while the MSDs of 
  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
  \end{figure}

@@

>>>>

\documentclass{article}

% Table of contents formatting
\usepackage{tocloft}

\renewcommand\cftsecfont{\normalfont}
\renewcommand\cftsecpagefont{\normalfont}
\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}}
\renewcommand\cftsecdotsep{\cftdot}
\renewcommand\cftsubsecdotsep{\cftdot}
\cftsetindents{section}{0em}{3em}
%\cftsetindents{subsection}{1em}{3em}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{array}
\usepackage{multirow}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

@@

  \maketitle
  \tableofcontents
  \graphicspath{{./supporting_figures/}}
  \bibliographystyle{ieeetr}

  \newpage

@@

  % mimic this
  \texttt{/setup/parameterize.py}            & 2.1 & Parameterize liquid crystal monomers and solutes with GAFF \\ \hline
  \texttt{/setup/build.py}                   & 2.1 & Build simulation unit cell \\ \hline
  \texttt{/setup/place\_solutes\_pores.py}   & 2.1 & Place equispaced solutes in the pore centers of a unit cell \\\hline
  \texttt{/setup/equil.py}                   & 2.1 & Equilibrate unit cell and run production simulation \\\hline
  \texttt{/analysis/solute\_partitioning.py} & 2.1 & Determine time evolution of partition of solutes between pores and tails \\\hline
  \texttt{/timeseries/msd.py}                & 2.2 & Calculate the mean squared displacement of solutes \\\hline
  \texttt{/analysis/sfbm\_parameters.py}     & 2.2 & Get subordinated fractional Brownian motion parameters by fitting to a solute's dwell and hop length distributions and positional autocorrelation function. \\\hline
  \texttt{/timeseries/ctrwsim.py}            & 2.2 & Generate realizations of a continuous time random walk with the user's choice of dwell and hop distributions \\\hline
  \texttt{/timeseries/forecast\_ctrw.py}     & 2.2 & Combines classes from \texttt{sfbm\_parameters.py} and \texttt{ctrwsim.py} to parameterize and predict MSD in one shot. \\\hline
  \texttt{/analysis/ markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
  \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD or MSDDM model. \\\hline

@@

  \begin{figure}[hb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_equilibration.pdf}
  \caption{}\label{fig:URE_equilibration}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_equilibration.pdf}
  \caption{}\label{fig:GCL_equilibration}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_equilibration.pdf}
  \caption{}\label{fig:ACH_equilibration}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_equilibration.pdf}
  \caption{}\label{fig:MET_equilibration}
  \end{subfigure}
  \caption{We considered a system to be equilibrated when the partition of solutes
  between the tails and pore plateaued. Our chosen equilibration point for each
  solute is indicated by the vertical black dashed line. (a) Urea equilibrates
  the fastest, after 1000 ns. (b) Ethylene glycol equilibrates after 1200 ns 
  (c) The partition of acetic acid appears oscillate slowly. We considered it to be
  equilibrated after 2000 ns. (d) We considered methanol to be equilibrated after
  3500 ns. Methanol nearly completely partitions into the tails.}\label{fig:equilibration}
  \end{figure}

@@

  \newpage

  \section{Estimating the Hurst Parameter}\label{section:H_estimate}

@@

  % /supporting_figures/hurst_autocorrelation.py
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{hurst_autocorrelation.pdf}
  \caption{}\label{fig:hurst_autocorrelation}
  \end{subfigure}
  % supporting_figures/flm_autocov.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flm_autocovariance.pdf}
  \caption{}\label{fig:flm_autocorrelation}
  \end{subfigure}
  \caption{(a) The analytical autocorrelation function of FBM decays to zero faster
  when H $<$ 0.5 compared to when H $>$ 0.5. (b) The autocorrelation function of an 
  FLM process does not change with increasing sequence length (N). It shares the same
  autocorrelation function as fractional Brownian motion (FBM). All sequenced used to
  make this plot were generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:hurst_parameters}
  \end{figure}

  The autocovariance function of fractional L\'evy motion is different from fractional
  Brownian motion (see Equations~\ref{M-eqn:fbm_autocorrelation}
  and~\ref{M-eqn:flm_autocovariance} of the main text), but their autocorrelation 
  structures are the same. The autocovariance function of FLM is dependent on the 
  expected value of squared draws from the underlying L\'evy distribution, $E\big[L(1)^2\big]$. 
  This is effectively the distribution's variance, which is undefined for most 
  L\'evy stable distributions due to their heavy tails. As a consequence, one should 
  expect $E\big[L(1)^2\big]$ to grow as more samples are drawn from the distribution
  with the autocovariance function responding accordingly. 
  However, we are only interested in the autocorrelation function. In order to predict
  the Hurst parameter from the autocorrelation function, we must show that it has 
  a well-defined structure and is independent of the coefficient in 
  Equation~\ref{M-eqn:flm_autocovariance} of the main text. In Figure~\ref{fig:flm_autocorrelation}, 
  we plot the average autocorrelation function from an FLM process with an increasing 
  number of observations per generated sequence. For all simulations we set $H$=0.35 
  and $\alpha$=1.4. The variance-normalized autocovariance function, i.e. the autocorrelation
  function, does not change with increasing sequence length. Additionally, the
  autocorrelation function of FBM, with the same $H$, is the same. Therefore we are 
  confident that we can use the same Hurst parameter as an input to both FBM and FLM
  simulations.

  \newpage

@@

@@

  \textit{Determining where to truncate the hop distribution:} A pure
  L\'evy stable distribution has heavy tails which can lead to arbitrarily
  long hop lengths. Our distribution of hop lengths fits well to a L\'evy
  distribution near the mean, but under samples the tails. In 
  Figure~\ref{fig:truncation_correction} we compare the empirically 
  measured transition emission distribution of the MSDDM for urea to its maximum likelihood fit to
  a L\'evy stable distribution. The ratio between the two distributions 
  at each bin is nearly 1 close to the center, indicating a near-perfect
  fit, larger than 1 slightly further from the center, suggesting that 
  we slightly over sample intermediate hop lengths, and below 1 far from 
  the center, indicating under sampling of extremely long hop lengths.
  Based on the plot, we chose a cut-off of 1 nm in order to compensate for
  over sampled intermediate hop lengths. We chose the same cut-off for all
  solutes.

  This procedure is complicated by the correlation structure of FLM. At a high level,
  Stoev and Taqqu use Riemann-sum approximations of the stochastic integrals defining
  FLM in order to generate realizations.~\cite{stoev_simulation_2004} They do this efficiently with the help of 
  Fast Fourier Transforms. In practice, this requires one to Fourier transform a zero-padded
  vector of random samples drawn from the appropriate L\'evy stable distribution, multiply
  the vector in Fourier space by a kernel function and invert back to real space. The end
  result is a correlated vector of fractional L\'evy noise.

  We are unaware of a technique for simulating truncated FLM, therefore we devised our
  own based on the above discussion. If one is to truncate an FLM process, one can apply
  the simple procedure above for drawing uncorrelated values from the marginal L\'evy 
  stable distribution, \textit{but}, after adding correlation, the maximum drawn value is typically lower than the limit set 
  by the user. Additionally, the shape of the distribution itself changes. Therefore, 
  we created a database meant to correct the input truncation parameter (the maximum desired draw). The database
  returns the value of the truncation parameter that will properly truncate the
  output marginal distribution based on $H$, $\alpha$ and $\sigma$ (the width parameter).
  Figure~\ref{fig:truncation_correction} shows the result of applying our correction.
  Note that generating this database requires a significant amount of simulation and
  still likely doesn't perfectly correct the truncation parameter. The output leads
  to a somewhat fuzzy, rather than abrupt, cut-off of the output distribution. This 
  is likely beneficial since we observe a small proportion of hops longer the chosen
  truncation cut-off. When the cut-off value is close to the L\'evy stable $\sigma$ parameter,
  as it is in our anomalous diffusion models, we observed that the tails of the 
  truncated distribution tend to be undersampled. In order to maintain the distribution's 
  approximate shape up to the cut-off value we recommend ensuring that the cut-off
  value is at least 2 times $\sigma$. However, this may lead to a slight over-prediction
  of the MSD.

  \newpage

@@

  To derive an analytical equation for the mean first passage time 
  (Equation~\ref{M-eqn:passage_times} of the main text), first consider an 
  initial pulse spreading out over time with a fixed mean. We can solve for the 
  time-dependent probability density of particle positions, $p$, by solving the one
  dimensional diffusion equation:
  \begin{equation}
  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
  \end{equation}
  The appropriate initial and boundary conditions are:
  $$BC1: t > 0, z = \infty, p = 0$$
  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
  $$IC: t = 0, c = M\delta(z)$$
  where $M$ is the total number of particles in the system. It has been shown 
  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
  \end{equation}
  We can make the substitution $z = z - vt$, where $v$ represents a constant average
  velocity, in order to linearly shift the mean as a function of time:
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
  \end{equation}
  One can track the fraction of particles, $F$, that have crossed the pore 
  boundary by integrating:
  \begin{equation}
  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
  \end{equation}
  where $L$ is the pore length. This represents the cumulative first passage 
  time distribution so we take its derivative in order to arrive at the first
  passage time distribution:
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. We calculated the
  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT. Specifically,
  we used the python package \texttt{scipy.integrate.quad} to numerically integrate:
  \begin{equation}
  E[t] = \int_0^\infty tP(t) dt
  \end{equation}

  \newpage

@@

  Analagous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
  Figures~\ref{fig:GCL_anticorrelated_hops}--\ref{fig:MET_anticorrelated_hops} 
  demonstrate that all solutes exhibit the same kind of anti-correlated hopping
  and trapping behavior.

  \begin{figure}[h]
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_trajectories.pdf}
  \caption{}\label{fig:GCL_solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/distributions_sfbm.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:GCL_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_powerlaw.pdf}
  \caption{}\label{fig:GCL_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_hop_acf.pdf}
  \caption{}\label{fig:GCL_hop_acf}
  \end{subfigure}
  \caption{For ethylene glycol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions. 
  See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
  in the main text for a more detailed discussion.}\label{fig:GCL_anticorrelated_hops}
  \end{figure}

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_trajectories.pdf}
  \caption{}\label{fig:ACH_solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/distributions_sfbm.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
  \caption{}\label{fig:ACH_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
  \caption{}\label{fig:ACH_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
  \caption{}\label{fig:ACH_hop_acf}
  \end{subfigure}
  \caption{For acetic acid: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions.
  See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
  in the main text for a more detailed discussion.}\label{fig:ACH_anticorrelated_hops}
  \end{figure}

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_trajectories.pdf}
  \caption{}\label{fig:MET_solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/distributions_sfbm.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
  \caption{}\label{fig:MET_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
  \caption{}\label{fig:MET_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
  \caption{}\label{fig:MET_hop_acf}
  \end{subfigure}
  \caption{For methanol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions.
  See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
  in the main text for a more detailed discussion.}\label{fig:MET_anticorrelated_hops}
  \end{figure}

  \newpage

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
  \caption{Urea}\label{fig:URE_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
  \caption{Methanol}\label{fig:MET_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
  \end{subfigure}
  \caption{The ensemble of solute trajectories may be stationary if the MSD
  calculated from different portions of the trajectory are the same. Here we
  plot the MSD calcluated up to a 500 ns time lag of the first and second
  halves of the equilibrated solute trajctories. Urea and acetic acid have
  similar MSDs, providing evidence of stationarity, while the MSDs of 
  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
  \end{figure}

  \newpage

@@

  The tables in the section are tabular representations of the parameters depicted
  in Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the 
  main text.

@@

  \newpage

@@

  The following table is a tabular representation of the parameters 
  depicted in Figure~\ref{M-fig:msddm_parameters} of the main text.
